%----------------------------------------
% SECTION TITLE
%----------------------------------------

\cvsection{Professional Experience}

%----------------------------------------
% SECTION CONTENT
%----------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Cloud Backend Developer} % Job title
{RINA S.p.A.} % Organization
{Genoa, Italy} % Location
{Nov. 2024 -- Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
  \item {Responsible for developing a serverless Python backend on Azure Functions for RINA's digital certification platform, primarily serving steel mill clients to certify their environmental sustainability efforts.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Junior Full Stack Developer} % Job title
{Rulex Innovation Labs} % Organization
{Genoa, Italy} % Location
{Nov. 2021 -- Oct. 2024} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
  \item {As part of the software development team, handled inter-service messaging, REST API implementation, and DevOps activities, and built/maintained the CLI for the Rulex Platform.}
  \item {Built and maintained CI/CD pipelines using Azure DevOps Pipelines.}
  \item {Deployed and tested cloud infrastructure with Terraform and Kubernetes.}
  \item {Developed primarily in Python and JavaScript (Node.js and React), including C++ plugins invoked from Python.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{University Teaching Assistant} % Job title
{University of Genoa} % Organization
{Genoa, Italy} % Location
{Sep. 2019 -- Sep. 2021} % Date(s)
{ % Description(s)
\begin{cvitems}
  \item {Delivered lectures and guided exercises for the General Physics course aimed at Chemical and Electrical Engineering students.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{University Tutor} % Job title
{University of Genoa} % Organization
{Genoa, Italy} % Location
{Sep. 2017 -- Sep. 2018} % Date(s)
{ % Description(s)
\begin{cvitems}
  \item {Provided tutoring in General Physics, Mathematical Analysis, and Linear Algebra to first-year Physics and Mathematics students, enhancing communication and interpersonal skills.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
