%----------------------------------------------------------------------------------------
% SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects and Technical Experience}

%----------------------------------------------------------------------------------------
% SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Developer} % Role
{SEYFERT: the SurvEY FishEr foRecast Tool} % Project
{Python, NumPy, SciPy, Pandas, Matplotlib} % Technologies
{2023 -- Present} % Date(s)
{ % Description(s)
\begin{cvitems}
  \item {Open-source Python tool for Fisher matrix forecasting of cosmological surveys.}
  \item {Cosmological analysis and predictions using advanced statistical methods and optimized numerical integration.}
  \item {Repository: \url{https://github.com/LucaPaganin/SEYFERT}}  
\end{cvitems}
}

%------------------------------------------------

\cventry
{Developer} % Role
{Solar System Simulator} % Project
{C++, Python, Dash} % Technologies
{2022 -- Present} % Date(s)
{ % Description(s)
\begin{cvitems}
  \item {Simulator of solar system dynamics with 3D animation of planetary orbits.}
  \item {Numerical integration in C++ and web interface developed with Dash.}
  \item {Repository: \url{https://github.com/LucaPaganin/SolarSystem/}}  
\end{cvitems}
}

%------------------------------------------------

\cventry
{Developer} % Role
{WebScraping Suite} % Project
{Python, HTML, JavaScript} % Technologies
{2021 -- Present} % Date(s)
{ % Description(s)
\begin{cvitems}
  \item {Collection of web scraping and data processing tools, including a Chrome extension for property listings and API scrapers for immobiliare.it.}
  \item {Supports data storage in CSV, SQLite, Azure Cosmos DB, and JSON formats.}
  \item {Repository: \url{https://github.com/LucaPaganin/webscraping}}  
\end{cvitems}
}

%------------------------------------------------

\cventry
{Developer} % Role
{Personal Website} % Project
{Next.js, TypeScript, Tailwind CSS, DaisyUI, Framer Motion} % Technologies
{2023 -- Present} % Date(s)
{ % Description(s)
\begin{cvitems}
  \item {Multilingual personal website with dark mode, responsive design, and interactive components (timeline, carousel).}
  \item {Content managed via Markdown and JSON, integrated with next-intl for internationalization.}
  \item {Repository: \url{https://github.com/LucaPaganin/personal-website}}  
\end{cvitems}
}

%------------------------------------------------

\cventry
{Developer} % Role
{Collectify} % Project
{Python, Flask, HTML, JavaScript, CSS} % Technologies
{2023 -- Present} % Date(s)
{ % Description(s)
\begin{cvitems}
  \item {Flask web application for aggregating and presenting user data using dynamic templates and static assets.}
  \item {MVC architecture with routing defined in app.py and templates/static assets management.}
  \item {Repository: \url{https://github.com/LucaPaganin/collectify}}  
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
